Uranyl solvation by a three-dimensional reference interaction site model

### 2015-04-17 doc/uo2_paper/uo2-II.tex
AM: PG ref, the, preprint layout

%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,journal=jpcafh,layout=twocolumn,maxauthors=0]{achemso}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{esint}
\usepackage[numbers]{natbib}

@@

All-electron QM calculations were carried out with the linear combination
of Gaussian-type orbitals fitting-functions density functional method
\citep{Dunlap90} as implemented in the parallel DFT code ParaGauss
\citep{ParaGaussV3.2}.  The atomic approximation \citep{Matveev08}
to the second-order Douglas\textendash{}Kroll\textendash{}Hess scalar-relativistic
approach \citep{rev:roesch96} was used to account for relativistic
effects; this approximation was shown to be very accurate for uranyl
aqua complexes \citep{Matveev08}. We employed the gradient-corrected
exchange-correlation functional (generalized gradient approximation,
GGA) \citep{Goerling99,kochDFT}, as suggested by Becke and Perdew
(BP) \citep{Becke88,Perdew86c}. The Kohn\textendash{}Sham orbitals
were represented by flexible Gaussian-type basis sets, contracted
in a generalized fashion using atomic eigenvectors. For U, we used
a basis set of the size (24s, 19p, 16d, 11f), contracted to {[}10s,
7p, 7d, 4f{]}; O and H atoms were described by standard basis sets,
(9s, 5p, 1d) $\to$ {[}5s, 4p, 1d{]} and (6s, 1p) $\to$ {[}4s, 1p{]},
respectively. These basis sets and further computational details are
the same as in earlier studies on uranyl species \citep{Moskaleva04,Moskaleva06b,Moskaleva06a,Kremleva12b,Bo15}.

@@

\begin{centering}
\begin{tabular}{lrrrr}
\hline 
 & \multicolumn{2}{c}{MM+RISM} &  & QM+RISM\tabularnewline
\cline{2-3} \cline{5-5} 
 & soft & hard &  & \tabularnewline
\hline 
$G(q^{\ast})$ & -426.0 & -430.8 &  & -434.4\tabularnewline
$G(q^{\#})$  & -423.7 & -426.5 &  & -425.2\tabularnewline
$G(0)$ & -426.1 & -427.2 &  & -428.7\tabularnewline
$\Delta G^{\#}$$^{b}$ & 2.3 & 4.3 &  & 9.1\tabularnewline
\end{tabular}
\par\end{centering}

@@

The transition state approximated by the structure with the highest
free energy is characterized by $q>0.6$~Å for both the QM and the
``soft'' uranyl models, with the longest U--O$_{\text{w}}$ distances
at 303~pm and 310~pm, respectively. These distances are comparable
to or slightly below the estimates derived above from the 1D and 3D
PMFs. The ``hard'' uranyl model, on the other hand, suggests a transition
state with a much shorter distance to the outermost water ligand of
\textasciitilde{}280~pm and a shallow metastable state. This is likely
a consequence of the significantly longer U--O bond of the solvated
uranyl species, \textasciitilde{}186~pm, which is more than 6~pm
longer than the corresponding distances of the other models employed
here and in other works \citep{Tiwari14,Kerisit13}. This particular
elongation should be considered as deficiency of the parametrization.
 In turn, the ``soft'' model does not convincingly show the preference
for five-coordinated uranyl with the sixth water in the second solvation
shell over the six-coordinated broken symmetry metastable structure.
The QM model and ``hard'' force field model predict the six-coordinated
$D_{3\text{d}}$-like state by 5.6~kcal/mol and 3.6~kcal/mol, respectively
(Table~\ref{tab:stationary-points}), less stable than the five-coordinated
structure with an extra water in the second shell. The presence of
such a six-coordinated intermediate may be taken to suggest an associative
two-step water exchange mechanism. This latter finding is consistent
with the results of other theoretical studies \citep{Tsushima07,Vallet01,Buehl06b,Rotzinger07,Tiwari14}
that suggest an associative mechanism as more favorable than the dissociative
mechanism via the four-coordinated intermediate structure.

@@

\bibitem{ParaGaussV3.2}

@@

  M\"{u}nchen, 2014.

>>>>

%% LyX 2.0.6 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english,journal=jpcafh,manuscript=article,layout=twocolumn,maxauthors=0]{achemso}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{esint}
\usepackage[numbers]{natbib}

@@

All-electron QM calculations were carried out with the linear combination
of Gaussian-type orbitals fitting-functions density functional method
\citep{Dunlap90} as implemented in the parallel DFT code ParaGauss
\citep{ParaGaussV4.0}.  The atomic approximation \citep{Matveev08}
to the second-order Douglas\textendash{}Kroll\textendash{}Hess scalar-relativistic
approach \citep{rev:roesch96} was used to account for relativistic
effects; this approximation was shown to be very accurate for uranyl
aqua complexes \citep{Matveev08}. We employed the gradient-corrected
exchange-correlation functional (generalized gradient approximation,
GGA) \citep{Goerling99,kochDFT}, as suggested by Becke and Perdew
(BP) \citep{Becke88,Perdew86c}. The Kohn\textendash{}Sham orbitals
were represented by flexible Gaussian-type basis sets, contracted
in a generalized fashion using atomic eigenvectors. For U, we used
a basis set of the size (24s, 19p, 16d, 11f), contracted to {[}10s,
7p, 7d, 4f{]}; O and H atoms were described by standard basis sets,
(9s, 5p, 1d) $\to$ {[}5s, 4p, 1d{]} and (6s, 1p) $\to$ {[}4s, 1p{]},
respectively. These basis sets and further computational details are
the same as in earlier studies on uranyl species \citep{Moskaleva04,Moskaleva06b,Moskaleva06a,Kremleva12b,Bo15}.

@@

\begin{centering}
\begin{tabular}{lrrrr}
\hline 
 & \multicolumn{2}{c}{MM+RISM} &  & QM+RISM\tabularnewline
\cline{2-3} \cline{5-5} 
 & soft & hard &  & \tabularnewline
\hline 
$G(q^{\ast})$ & -426.0 & -430.8 &  & -434.4\tabularnewline
$G(q^{\#})$  & -423.7 & -426.5 &  & -425.2\tabularnewline
$G(0)$ & -426.1 & -427.2 &  & -428.7\tabularnewline
$\Delta G^{\#}$$^{b}$ & 2.3 & 4.3 &  & 9.1\tabularnewline
\hline
\end{tabular}
\par\end{centering}

@@

The transition state approximated by the structure with the highest
free energy is characterized by $q>0.6$~Å for both the QM and the
``soft'' uranyl models, with the longest U--O$_{\text{w}}$ distances
at 303~pm and 310~pm, respectively. These distances are comparable
to or slightly below the estimates derived above from the 1D and 3D
PMFs. The ``hard'' uranyl model, on the other hand, suggests a transition
state with a much shorter distance to the outermost water ligand of
\textasciitilde{}280~pm and a shallow metastable state. This is likely
a consequence of the significantly longer U--O bond of the solvated
uranyl species, \textasciitilde{}186~pm, which is more than 6~pm
longer than the corresponding distances of the other models employed
here and in other works \citep{Tiwari14,Kerisit13}. This particular
elongation should be considered as deficiency of the parametrization.
 In turn, the ``soft'' model does not convincingly show the preference
for five-coordinated uranyl with the sixth water in the second solvation
shell over the six-coordinated broken symmetry metastable structure.
The QM model and the ``hard'' force field model predict the six-coordinated
$D_{3\text{d}}$-like state by 5.6~kcal/mol and 3.6~kcal/mol, respectively
(Table~\ref{tab:stationary-points}), less stable than the five-coordinated
structure with an extra water in the second shell. The presence of
such a six-coordinated intermediate may be taken to suggest an associative
two-step water exchange mechanism. This latter finding is consistent
with the results of other theoretical studies \citep{Tsushima07,Vallet01,Buehl06b,Rotzinger07,Tiwari14}
that suggest an associative mechanism as more favorable than the dissociative
mechanism via the four-coordinated intermediate structure.

@@

\bibitem{ParaGaussV4.0}

@@

  M\"{u}nchen, 2012.
